\fraktursection{Berlin, 22 December 1962}

I have travelled through oceans of time, across the corpses of countless forgotten worlds, and through the endless, starless voids between.
It was a brutal itinerary, a pilgrimage of suffering, each step a sacrifice upon the altar of a singular, sacred vow: to find her.

My arrival was a disorienting violence, a jarring transition from the timeless beauty of Barovia into a world polluted by man.
A world of concrete and steel, of smoke and noise, where cold lights pierce the night like artificial stars, powered by diesel, petrol, and coal.
The galaxy, the luminous spine of the night, is smothered by a shroud of industrial haze, echoing the cold illumination of the city.
Their buildings rise like great, weathered cliff faces, their repetitive facades holding the quiet lives of thousands; a soul-crushing monotony, a deliberate insult to the solitary grandeur of my castle.

The noises of this world assault my ancient senses: the distant rumble of trams trundling down Karl-Marx-Allee, the clatter of U-Bahn trains beneath the streets, the ceaseless hum of factories, and the sharp blare of a horn or siren.
The air is thick with the scent of a world in motion: the crisp, metallic tang of coal dust warming a thousand homes, the earthy smell of damp limestone from the U-Bahn tunnels, and the faint, greasy aroma of frying Spreewaldgurken from a corner Imbiß.

A sudden gust of wind, chill and biting, carries a forgotten clarity.
Within this unfamiliar brew, it brings back a memory, faint and elusive as a phantom pain, of the old Barovia; the crisp, cold air that would sweep down from the Balinoks before the mists came.
This potent bitterness hones my thoughts.
A hunger for control, which millennia of repetition and countless cycles of death and rebirth had worn dull, awakens and stretches its claws within me.

This time, it will be different.
This time, I will make her mine.

I am not the Land here, no.
The soil does not whisper my name, nor do the shadows answer my summons with the same fervent obedience.
The river is not a loyal servant, but an adversary that tries to block my passage.
The forests do not bow to my will, but stand as silent sentinels, indifferent to my ancient claims.
I am a relic in a world that has built its own, formidable magic from coal, diesel, steel, and collective will.
But I am Strahd von Zarovich.
I will force this concrete forest to bend.
I will make this unwelcoming city my domain.
And Tatyana, wherever she hides within its labyrinthine courtyards and humming factories, will be my queen.

Upon my arrival, there was another traveller.
An enigmatic figure, cloaked in an unsettling familiarity, who moved with the quiet assurance of one who knows all the secrets of this particular labyrinth.
He claimed to know the true me.
He spoke in riddles, his tone mildly provoking, laced with a knowing amusement as if my eternal hunt was a quaint, predictable drama.
He implied I am but the latest in a long procession of desperate souls to wash up on these shores, all seeking something this world does not freely give.

I felt the old, cold rage stir.
But I did not endure all this pain merely to reveal my purpose in a poorly chosen battleground.
So, I let him go.

He provided me with the keys to a residence overlooking Alexanderplatz, a monumental plaza that is the vibrant, beating, bureaucratic heart of this world's ambition.
And an ID.
A service called Stasi, it reads.
My name is there, cold and official, alongside a number, and a department: Sondergruppe Dämmerung.

This, he asserted with an unnerving smirk, was the best place to begin my search.
In this world, he implied, one does not find souls through scrying, but through files.

``No Vistani here to guide you, no cursed lands to deliver her to your doorstep, Fürst,'' he whispered, the title a subtle mockery, ``you must find her yourself this time.''

Before I could seize him, he vanished as mysteriously as he appeared, with a swift, efficient grace that was not native to this place.
He was gone, leaving me alone with the cold wind that whipped across the vast plaza, a king without a kingdom, a hunter in a world where every shadow had been catalogued and every secret was considered state property.
The game was the same, but the board was terrifyingly new.

\vfill\newpage
