\fraktursection{Berlin, 30 October 1963}

Everything was ready for the big day.
The past few days were filled with preparations, feeding the Stasi with information about the cultural invasion of the West.
My plan had to be amended; the march would start at the Brandenburg Gate.
Nikolai is smart enough to avoid a direct confrontation when all eyes will be on us.

I made sure we were both assigned to patrol it, together with a small, elite team.
I was the first to arrive.
The Brandenburg Gate is no mere monument; it is a sentinel of stone, a relic of empires long crumbled, now shackled by the iron will of men.
I have stood before it often during my time here.
Tonight, cloaked in mist, it was a nostalgic reminder of my life back in Castle Ravenloft.
Its columns, weathered and solemn, rose like the ribs of a fallen titan, guarding a realm I could not breach.
The thick mist echoed the Western lights beyond the Wall, flickering and taunting me from a world that has moved on.
The Wall, cold and unyielding, had cleaved the Gate from its purpose, turning it into a ghost of a passage, a threshold denied.

I stood there, thinking of you, Tatyana.
I remember the slightest detail of your face, of your wedding dress.
I remember your eyes, your voice, all the names you have been born into all these years.
What is your name this time?

My thoughts were abruptly interrupted by footsteps.
Nikolai and the rest of our team were approaching.
I knew that not all of us would survive the night, but I needed the coroner's report to reach the right people.
``Genosse Strahd,'' one of them said, ``are you sure that your intel is good?''

``I do not understand why anyone would risk the gifts of socialism for a child's feast.
We saved the world from the Führer.
We have healthcare, the best education, housing for all.
We may even walk on the moon someday.
There is nothing these capitalist pigs can offer.
Yet people are risking their lives for what?''
As a man who has achieved immortality, I have a unique vantage point of the brevity of human life.

As soon as I tried to answer, the children of the night came out.
They marched toward the Gate, seeking shelter in the mist.
Their orders were clear.
Kill, and the more obvious the killing is done by an undead, the better.
I saw the team rushing to stop the march.
Nikolai stayed behind and told me we should clean up the mess.
He knew this was no costume.
I saw him light up with a pure blue light, the unmistakable radiance of an Irda.
What would an Irda have against me? Why would an Irda care about Tatyana? All these questions need an answer, but for now, I must act.

I rushed into the battle, but before fighting head-on against my children, I needed to ensure that the report would reveal the supernatural nature of this attack, not just to anyone, but to someone who would heed the clues.
I approached an injured comrade and drained him, making sure the teeth marks on his neck were obvious.

I will learn from this, and I will be ready.

\vfill\newpage
