\fraktursection{Berlin, 26 January 1963}

A moon has passed since my arrival in this city, and the shadows of Berlin have begun to reveal their secrets.
The Stasi, with its cold efficiency, has become a tool in my hands, a means to an end.
I have learned to navigate its labyrinthine bureaucracy, manipulating its agents to reveal the information I seek.
I have also met with the dissidents, the outcasts, and the delinquents; the true shadows of this society.
They are my eyes and ears, whispering to me in the dark corners of this concrete jungle.
They are not the Vistani, but they are useful nonetheless.

A month has passed, and I have yet to find Tatyana.
The Stasi's files yield no trace of her, but Nikolai and his minions are feeding me with leads.
This is a temporary advantage, perhaps, but I must tread carefully.
I have tasked my own spies to watch him, to learn his patterns and habits.
He is a ghost in the night, slipping through the fingers of those who seek him.

Today, I decided to assume my bat form and follow him.
I lost him, but I learned something.
He entered an alley, and the man who emerged on the other side was a typical, middle-aged, worn-out man with no recognizable characteristics.
He continued walking through the same alleys, forcing me to follow him dangerously close to dawn.
Did he sense my presence? Was this a trap, or a display of confidence? Regardless, I got a glimpse of his abilities, and I should be able to use that knowledge to my advantage.

I can feel the sunrise fast approaching, and I must return to my lair before the first rays of light pierce the sky.
For the sun is unforgiving, and my time is not yet at an end.

\vfill\newpage
