\fraktursection{Berlin, 22 October 1963}

My hunt for Tatyana has led me to the banks of the Spree river.
I stood there for a long time, a static observer, watching the water flow past.
Its surface, a black mirror, reflected a million diamonds, a silver road forged by the moon's light.
I could feel the presence of the city on the other side, so close, yet so physically demanding that I do not cross unless absolutely necessary.

I despise this river, this unforgiving current that reminds me of my eternal confinement, of a freedom I can never possess.
I have crossed planes, conquered kingdoms, and defied the boundaries of time, but crossing this simple stream requires all my willpower.

Yet, on a chill night like tonight, it possesses a mesmerizing beauty.
I walked closer and touched a bouquet of roses.
Next to it, on a bench, a freshly carved heart: ``Für Olga. Immer und ewig, Alexander.''
It is so amusing what humans consider everlasting love.
I touched it, and I watched its life escaping, withering and turning into dust—dust that was blown away by the gentle autumn breeze.
I closed my eyes, took a deep breath, and tried to feel all the city's smells.

And then, I felt her.
A woman walking on the other side of the river, her scarf pulled high against the wind.
For a moment, I thought I saw her eyes—her eyes—but by the time I managed to cross, she had vanished between the buildings before I could be certain.
The street swallowed her, as it swallows all things here.

My frustration left a bitter taste in my mouth, a constant reminder of my helplessness.
The chill breeze lost its refreshing feel, becoming sickening and nauseating.
I was lost in the dark alleys of this city, and I had to cross the river again to find my way back.

Walking back, I decided upon a new gambit.
We are fast approaching the first anniversary of my arrival on this plane, and I must act quickly.
I must be conscious of time, not for its effect on me, but rather for the lack of it.
I cannot afford any unwanted attention towards me.
Nikolai and I cannot be the only travelers, and I need to see the whole picture.
I need to find allies, and in a few days, there is a Western celebration: Halloween.
There is no better time for some classic necromancy, easily blamed by the Stasi as a capitalist culture war.
An undead parade next to their headquarters might also reveal Nikolai's true identity.

\vfill\newpage
