\fraktursection{Berlin, 1 January 1965}

After all these years, I found her.
Tatyana was there, as beautiful as ever, on the stage of a small underground club.
Her voice, a haunting melody that echoed through the dimly lit room, stirred something deep inside me.
Finally, she was within my grasp.
I felt the weight of destiny, so close to reclaiming what was mine that I hesitated for just one fateful moment.

Then, everything changed.
The club was raided by the Stasi, their heavy boots thudding against the wooden floor, their shouts piercing the air.
Nikolai Volkov, shouting orders over the chaos.
Tatyana managed to escape, and I gave chase, but Nikolai followed, running after us both.
I knew it was time to deal with him.
I had read Tatyana's thoughts; she was heading towards Checkpoint Charlie.
I had to stop Nikolai, and I had to find Tatyana.

I confronted him in the narrow alley behind the club, the sirens wailing in the distance.
A mist, thick and suffocating, was forming around us.
Nikolai stood there and finally revealed his true nature.
``Do not act so surprised, brother,'' he said, his voice low and mocking.
``Did you truly think that Tatyana was the only one trapped in this never-ending cycle?''

I attacked him swiftly, and I could have ended him, but I needed to know more.
``What do you mean?'' I demanded, my fangs bared.
``You and I, we are bound by blood, Strahd,'' he said, his deep sapphire eyes radiating a pale light.
``I am your brother, Sergei.
The one you killed.
The one you betrayed.
The one you thought was dead.
But as Tatyana is reborn, so am I.
We are bound by the same curse, the same cycle of pain and loss.
But this time, I will not be your pawn.
I will not be trapped in your shadow.
This time, it is my turn to haunt you.
I am no longer Sergei von Zarovich; I am Nikolai Volkov, the son of the wolf.
I am the hunter, not the prey.''

I was stunned.
My brother, alive? I had thought him dead for centuries, a victim of my own hand.
The realisation hit me like a blow to the chest.
``You are not my brother,'' I hissed, my voice low and dangerous.
``You are a shadow of what you once were, a twisted reflection of my past.''
I bit him, my fangs sinking deep into his neck.
He screamed, but as soon as I began to drain him, a foul taste filled my mouth.
I pulled back, disgusted.
``You are not my brother,'' I repeated, spitting the blood onto the ground.
``You are nothing but a monster.''

Nikolai laughed, a cold, mirthless sound that echoed through the alley.
``I had to accept lycanthropy, not as a curse, but as a gift,'' he said.
``My Irda blood and the gift of lycanthropy allowed me to become something stronger.
This day is the day I will reunite with Tatyana.''
His skin echoed the light of the moon, smooth as polished marble, but supple as mist-woven silk.
He attacked me with such ferocity that I fell, my back hitting the cold, hard pavement.
I tried to stand, but he was already on top of me.

``Ravenloft was your prison, brother.
Berlin will be your grave.''
He raised his hand, holding a small, ornate dagger that glinted in the dim light.
I had to summon all my strength to turn into a swarm of bats and fly toward the checkpoint, leaving Nikolai behind.
I could see him transform into a wolf, chasing after me, but I was faster.

After a short flight, I arrived at Checkpoint Charlie.
The place was a chaotic mess, with Stasi agents and civilians alike trying to escape.
I spotted Tatyana, running past the checkpoint to her freedom.
I tried to reach her, but the Wall would not let me through.
I could only watch as she disappeared into the night, her figure swallowed by the shadows.

Shouts and gunfire erupted as the Stasi laid blame for the escape.
Everyone was to be punished.
For the next few moments, everyone paid for it.
The smell of blood filled the air, and I made sure that no one would live to see another day.

I returned to my apartment.
My brother was right.
Ravenloft was my prison.
I was not the Land there, just a prisoner in a never-ending cycle of despair and loss.
And here, in this soul-crushing city, I was trapped once again.
But tomorrow, I will be free.

I stood looking at the empty mirror, the one the Vistani had given me.
My ticket to another plane, a chance to start anew.
A new beginning, without Sergei, without Tatyana, without the endless cycle of pain and loss.
I could leave this place behind and never look back.
Castle Ravenloft would be nothing but a distant memory.
But would I ever be free this way? I would flee, but that would make me the prey, and I am not prey.
I am the hunter.

Looking back, the first time I scried upon this plane, men hunted with spears, unable even to use iron.
Here, everything has evolved.
Berlin, in its own way, is a monument to technology.
All these advances that we could not even dream of, back in Barovia.
Frozen in time, we are cursed to relive the same story again and again and again.

Perhaps my freedom is finally meeting the sun.
I have not felt the warm rays of the sun on my skin for centuries.
I could just step into the light, embrace its sweet warmth, and finally be free.
I could end this cycle of pain and loss, once and for all.
And yet, there are no guarantees.
Will I be free, or will I just find myself in another prison? Will the three of us be reunited again, pawns in some cosmic game of fate?

\vfill\newpage
